---
title: "Developmental and postural changes in children's visual access to faces"
bibliography: xsface.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{{\large \bf Alessandro Sacnhez} \\ \texttt{author1@university.edu} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Bria Long} \\ \texttt{bria@stanford.edu} \\ Department of Psychology \\ Stanford University
        \And {\large \bf Ally Kraus} \\ \texttt{bria@stanford.edu} \\ Department of Psychology \\ Stanford University
        \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

abstract: 
     The faces of other people are a critical information source for young children. During early development, children undergo significant postural and locomotor development, changing from lying and sitting infants to toddlers who walk independently. We used a head-mounted camera in conjunction with a face-detection system to explore the effects of these changes on children's visual access to their caregivers' faces during an in-lab play session. In a cross-sectional sample of 8--16 month old children, we found substantial changes in face accessibility based on age and posture. These changes may translate into changes in the accessibility of social information during language learning. We make our corpus available for reanalysis, and discuss strengths and limitations of the headcam method more generally.
    
keywords:
    "social cognition; face-perception; infancy; locomotion; head-cameras"
    
output: cogsci2016::cogsci_paper
---

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, message=F, sanitize = T)
```

```{r, libraries}
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=TRUE, message = FALSE, sanitize = TRUE)
library(readr)
library(dplyr)
library(tidyr)
library(xtable)
library(lubridate)
```

# Methods


## Participants

```{r echo=FALSE, include=FALSE}
all_subs <- read.csv("../data/demographics/all_participants.csv") %>%
  rename(subid = subID)
inc_subs <- read.csv("../data/demographics/demographics.csv")
all_subs$inc <- all_subs$reason=="included"

inc_subs$len.min <- sapply(strsplit(as.character(inc_subs$len),":"),
       function(x) {
         x <- as.numeric(x)
         x[1]+x[2]/60
       }
)

all_subs %>% 
  group_by(reason) %>%
  summarise(n = n()) %>% 
  kable

# # exclusions by age
# all_subs %>% 
#   group_by(reason, age_group) %>%
#   summarise(n = n()) %>%
#   spread(age_group, n) %>%
#   xtable %>%
#   print(digits = 2)


all_subs %>%
  left_join(inc_subs) %>%
  group_by(age_group) %>%
  summarise(n = sum(inc), 
            percent_included = mean(inc),
            age = mean(age.at.test, na.rm=TRUE), 
            video_length = mean(len.min, na.rm=TRUE), 
            female = mean(gender=="female", na.rm=TRUE)) %>%
  xtable %>%
  print(digits = 2, include.rownames=FALSE)
```

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
Age group & N & \% included & Mean age & Video length (min) & \% female \\ 
  \hline
   8 &  12 & 0.46 & 8.71 & 14.41 & 0.50 \\ 
   12 &  12 & 0.40 & 12.62 & 13.48 & 0.58 \\ 
   16 &  12 & 0.31 & 16.29 & 15.00 & 0.50 \\ 
   \hline
\end{tabular}
\caption{\label{tab:pop} Demographics by age group.}
\end{table}

Our final sample consisted of 36 infants and children, distributed into each of three age groups: 8 months, 12 months, and 16 months. Participants were recruited from the surrounding community via state birth records. Participants had no documented disabilities and were reported to hear at least 80\% English at home. Demographics and exclusion rates are given in Table \ref{tab:pop}. 

In order to compile this final sample, we tested a substantially larger group of children, who were excluded for the following reasons: 
`r sum(all_subs$reason=="HC technical error")` for technical issues related to the headcam,
`r sum(all_subs$reason=="would not wear camera")` for failing to wear the headcam,
`r sum(all_subs$reason=="less than 4 min HC footage")` for fewer than 4 minutes of headcam footage,
`r sum(all_subs$reason=="multiple people")` for having multiple adults present,
`r sum(all_subs$reason=="no CDI")` for missing CDI data,
`r sum(all_subs$reason=="no DV cam footage")` for missing scene camera footage,
`r sum(all_subs$reason=="infant crying")` for fussiness, and one excluded for sample symmetry. All inclusion decisions were made independent of the results of subsequent analyses.
```

# Acknowledgements

"Thanks to Ally Kraus, Kathy Woo, Aditi Maliwal, and other members of the Language and Cognition Lab for help in recruitment, data collection, and annotation. This research was supported by a John Merck Scholars grant to MCF. An earlier version of this work was presented to the Cognitive Science Society in @frank2013. Please address correspondence to Michael C. Frank, Department of Psychology, Stanford University, 450 Serra Mall (Jordan Hall), Stanford, CA, 94305, tel: (650) 724-4003, email: \texttt{mcfrank@stanford.edu}."

# References 

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent
