---
title: "Franchak_ReAnalysis"
author: "Bria Long"
date: "3/5/2020"
output: html_document
---

# Preprocessing
## Libraries
```{r}
rm(list=ls()) # remove all objects from current workspace
library(ggthemes)
library(langcog)
library(tidyverse)
library(cowplot)
```

## Read in merging filenames data
```{r}
filenames <- read.csv('../data/franchak_dataset/meta/subID_matching.csv') %>%
  mutate(vid_name = str_split_fixed(VideoName,'.mp4',2)[,1]) %>%
  mutate(sub_id = SubID) %>%
  select(vid_name, sub_id)
```

## Read in position data and preprocess
```{r}
files = dir('../data/franchak_dataset/posture/')
all_pos_data=tibble()

for (s in files) {
  sub_id_short_temp = str_split_fixed(s, '-',2)[,2]
  sub_id_short = str_split_fixed(sub_id_short_temp, '_pos.csv',2)[,1]
  
this_sub_position_data <- read.csv(paste0('../data/franchak_dataset/posture/', s)) %>%
  as.tibble %>%
  mutate(frame = row_number(), sub_id = sub_id_short) %>%
  mutate(frame = frame - 1)  %>% ## openpose is 0 indexed
  rename('infant_posture' = 'NaN.', 'caregiver_posture' = 'NaN..1') %>%
  filter(!is.na(infant_posture)) 

all_pos_data <- bind_rows(all_pos_data,this_sub_position_data)
}

all_pos_data <- all_pos_data %>%
  mutate(sub_id = as.factor(sub_id))
```

## How much data do we have for each subject?
```{r}
(frames_by_sub <- all_pos_data %>%
  group_by(sub_id) %>%
  summarize(num_frames = length(unique(frame))) %>%
  kable())
```

## Read in detections and merge with subid from above
```{r}
csv_dir = paste0(here::here(),'/data/franchak_dataset/openpose_detections/csvs_compressed_with_conf/')
files = dir(csv_dir)
sub_count = 0

for (f in files){
  print(f)
  sub_count = sub_count + 1
  print(sub_count)
  this_sub <- read.csv(paste0(csv_dir,f)) %>%
    as.tibble() 
  
  if (sub_count==1){
     detections <- this_sub
  } else{
  detections <- detections %>%
    full_join(this_sub) 
  }
}

dets <- detections %>%
  mutate(vid_name = str_split_fixed(subid,'.json',2)[,1]) %>%
  select(-subid) %>%
  left_join(filenames) %>%
  mutate(sub_id = as.factor(sub_id)) %>%
  rename(frame = frame_num)

```

# Merge detections with position data (should merge on subid, frame)
```{r}
pos_detections  <- all_pos_data %>%
  left_join(dets, by=c('frame','sub_id')) 
```

### Recode variables so are redable
```{R}
level_key = c('0' = "Prone", '1' = "Sitting", '2' = "Upright")
pos_detections$caregiver_posture_label = recode(pos_detections$caregiver_posture, !!!level_key) 
pos_detections$infant_posture_label = recode(pos_detections$infant_posture, !!!level_key) 

pos_detections <- pos_detections %>%
  mutate(face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose))


```

### Save out preprocessed data
```{r}
# save(file = '../data/franchak_dataset/preprocessed/franchak_dataset_detections_july2020.RData', detections)
save(file = '../data/franchak_dataset/preprocessed/franchak_dataset_detections_by_posture_july2020.RData', pos_detections)

```

# Basic analyses
## Compute faces by infant posture
```{r}
faces_by_pos  <- pos_detections %>%
  group_by(sub_id, infant_posture_label) %>%
  dplyr::summarize(prop_faces = mean(face_openpose)) %>%
  group_by(infant_posture_label) %>%
  multi_boot_standard(col = 'prop_faces')

faces_by_pos_by_sub  <- pos_detections %>%
  group_by(sub_id, infant_posture_label) %>%
  summarize(prop_faces = mean(face_openpose))
```

## Plot detections by posture
```{r}
(faces_by_pos_plot <- ggplot(faces_by_pos, aes(x=infant_posture_label, y=mean, col=infant_posture_label)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
   geom_point(data=faces_by_pos_by_sub, aes(x=infant_posture_label, y=prop_faces, col=infant_posture_label), alpha=.2) +
  theme_few(base_size=18) +
  ylab('Prop faces detected') +
  xlab('Infant posture') + 
  ylim(c(0,.3)) +
  theme(legend.position = 'none') +
  scale_color_manual(name = "Posture", values=c("#339966","#eb7928","#0099cc"))) 


```

## Faces by caregiver posture 
```{r}
faces_by_CG_pos  <- pos_detections %>%
  group_by(sub_id, caregiver_posture_label) %>%
  summarize(prop_faces = mean(face_openpose)) %>%
  group_by(caregiver_posture_label) %>%
  multi_boot_standard(col = 'prop_faces') 
  
(ggplot(faces_by_CG_pos, aes(x=caregiver_posture_label, y=mean, col=caregiver_posture_label)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  theme_few())

```


## Look at hands by infant posture as well
```{r}
hands_by_pos  <- pos_detections %>%
  group_by(sub_id, infant_posture_label) %>%
  summarize(prop_hands = mean(hand_openpose)) %>%
  group_by(infant_posture_label) %>%
  multi_boot_standard(col = 'prop_hands')

hands_by_pos_by_sub  <- pos_detections %>%
  group_by(sub_id, infant_posture_label) %>%
  summarize(prop_hands = mean(hand_openpose))

```


```{r}
faces_by_both_pos  <- pos_detections %>%
  group_by(sub_id, infant_posture_label, caregiver_posture_label) %>%
  summarize(prop_faces = mean(face_openpose)) %>%
  group_by(infant_posture_label,caregiver_posture_label) %>%
  multi_boot_standard(col = 'prop_faces') 
  
(ggplot(faces_by_both_pos, aes(x=infant_posture_label, y=mean)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  theme_few() +
  facet_wrap(~caregiver_posture_label))

```

### Plot hands by infant posture
```{r}
(hands_by_pos_plot <- ggplot(hands_by_pos, aes(x=infant_posture_label, y=mean, col=infant_posture_label)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  geom_point(data=hands_by_pos_by_sub, aes(x=infant_posture_label, y=prop_hands, col=infant_posture_label), alpha=.2) +
  theme_few(base_size=18) +
  ylab('Prop hands detected') +
   xlab('Infant posture') + 
  ylim(c(0,.4)) +
  theme(legend.position = 'none') +
  scale_color_manual(name = "Posture", values=c("#339966","#eb7928","#0099cc")))

```


```{r}
cowplot::plot_grid(faces_by_pos_plot,hands_by_pos_plot)
```